---
title: 'Part 1: Data Cleaning'
author: "Rebekah Jacob"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE)
```

```{r}
library(openxlsx)
library(tidyverse)
```

# First comment df
```{r}
comment1_df<- read.xlsx("../First comment review/completed comments.xlsx") %>%
  select(-Column1)

head(comment1_df %>%
       select(-commentText))
nrow(comment1_df)
names(comment1_df)

```
# Second comment df
```{r}
comment2_df<- read.xlsx("../Second comment review/FNS-2020-0038_FOR_CODING_10.10.2022.xlsx")

head(comment2_df %>%
       select(-comment))
nrow(comment2_df)
names(comment2_df)
```


# First cleaning
## to lower stance and org_type
In the first round, broadened milk options, half whole-grain, more time for sodium reduction.

Most do NOT want these flexibilities "maintain current regulations".
```{r}
comment1_df<- comment1_df %>%
  mutate(stance_1=str_to_sentence(stance_1),
         org_type=str_to_sentence(org_type))

comment1_df %>%
  group_by(stance_1) %>%
  tally()
```

## Create new smaller categories for stance_1
```{r}
comment1_df<- comment1_df %>%
  mutate(stance_1_cat3=factor(case_when(
    stance_1=="Maintain current regulations"~"In favor of original HHFKA",
    stance_1 %in% c("Implement some of the new rules", "Do implement new rules")~"In favor of flexibilies",
    TRUE ~ "Other"), levels=c("In favor of original HHFKA", "In favor of flexibilies", "Other")))
```


## Assign constituent

A few form letters are from orgs, so we'll weed those out when we assign the rest of form letters to constituents
```{r}
nrow(
  comment1_df %>%
  filter(!is.na(dup_comment_num) & !is.na(organization_new))
)
```

Looks like we need to code N=5627.
```{r}
nrow(
  comment1_df %>%
  filter(!is.na(dup_comment_num) & is.na(organization_new))
)
```


```{r}

comment1_df %>%
  group_by(org_type) %>%
  tally()


comment1_df<- comment1_df %>%
  mutate(org_type=case_when(
    is.na(org_type) & is.na(organization_new)~"constituent",
    TRUE ~ as.character(org_type)
  ))



         
comment1_df %>%
  group_by(org_type) %>%
  tally()
```


## Factorize org
```{r}
comment1_df<- comment1_df %>%
  mutate(org_type=factor(org_type, levels = c(
    "Academic researchers",
    "Advocacy",
    "Constituent",
    "Manufacturer/food industry",
    "School",
    "Other government agency - (non school)",
    "Other"
    
  )))
```


## clean up var names

```{r}
comment1_df<- comment1_df %>%
  mutate(year=2017) %>%
  select(year, commentid=documentId, form_letter=dup_comment_num, org_type, comment=commentText, stance_1, stance_2, stance_1_cat3)
```



# Second cleaning

In the second round, they propose to roll-back standards again.

Most do NOT want these flexibilities "do not restore flexibilites"

```{r}

comment2_df<- comment2_df %>%
  mutate(stance_1=str_to_sentence(stance_1),
         org_type=str_to_sentence(org_type))

comment2_df %>%
  group_by(stance_1) %>%
  tally()
```

```{r}
comment2_df %>%
  group_by(org_type) %>%
  tally()
```


## Assign form letter info
```{r}
comment2_df<- comment2_df %>%
  mutate(form_letter=case_when(
    grepl("It is not productive to railroad this damaging rule through with only a 30-day comment period over the holidays", comment)~"Form 1a",
    grepl("It is harmful to railroad this damaging rule through with only a 30-day comment period over the holidays", comment)~"Form 1b",
    grepl("About 1 in 3 Latino families live in poverty and 1 in 4 are food insecure", comment)~"Form 2- Salud America!",
    grepl("Students discard the fat-free and low-fat milk then buy drinks devoid of nutrition and sweetened with a combination of high fructose corn syrup and artificial sweetener", comment)~"Form 3"
    ))
```

## Create new smaller categories for stance_1
```{r}
comment2_df<- comment2_df %>%
  mutate(stance_1_cat3=factor(case_when(
    stance_1=="Do not restore flexibilities"~"In favor of original HHFKA",
    stance_1 %in% c("Restore all flexibilities", "Restore some of the flexibilities")~"In favor of flexibilies",
    TRUE ~ "Other"), levels=c("In favor of original HHFKA", "In favor of flexibilies", "Other")))
```


## Factorize org
```{r}
comment2_df<- comment2_df %>%
  mutate(org_type=factor(org_type, levels = c(
    "Academic researchers",
    "Advocacy",
    "Constituent",
    "Manufacturer/food industry",
    "School",
    "Other government agency - (non school)",
    "Other"
    
  )))
```

## clean up var names
```{r}

comment2_df<- comment2_df %>%
  mutate(year=2020) %>%
  select(year, commentid=commentId, form_letter, org_type, comment, stance_1, stance_2, stance_1_cat3)

```



# Write clean sets for analysis
```{r}
write.csv(comment1_df, "first-round-comments.csv")
write_rds(comment1_df, "first-round-comments.rds")


write.csv(comment2_df, "second-round-comments.csv")
write_rds(comment2_df, "second-round-comments.rds")
```


