---
title: 'School Lunch Flexibilities: Federal Register Comments Analysis'
author: "Rebekah Jacob"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning=FALSE)
```


```{r}
library(tidyverse)
library(ggthemr)
ggthemr("light")
library(arsenal)
```

```{r}
com1df<- readRDS("first-round-comments.rds")

com2df<- readRDS("second-round-comments.rds")
```


# Introduction

This data was extracted from the Federal Register. Extensive cleaning was performed on the data to remove true duplicates and identify form letters. Organization names were coded into `org_type` from both the organization description and/or if revealed within the comment during the coding process.

Form letters (`form_letter`) were identified and sources were determined if available.

# Description {.tabset .tabset-pills}

## 2017
```{r results='asis'}

# controls for all Tableby tables throughout
mycontrols  <- tableby.control(test=FALSE, numeric.stats = c("meanCI"), digits=2L, cat.stats = c("countpct"))


mylabels <- list(org_type="Organization type",
                 stance_1="Main stance (coded comment)",
                 form_letter="Form letter source",
                 stance_1_cat3="Main stance (coded comment into 3 categories)")


desc1_tbl <- tableby(~
                    org_type +
                      stance_1 +
                      form_letter, data=com1df, control=mycontrols)

summary(desc1_tbl, labelTranslations = mylabels, pfootnote=TRUE)
```

## 2020
```{r results='asis'}
desc2_tbl <- tableby(~
                    org_type +
                      stance_1 +
                      form_letter, data=com2df, control=mycontrols)

summary(desc2_tbl, labelTranslations = mylabels, pfootnote=TRUE)
```

# Support for flexibilities {.tabset .tabset-pills}
## 2017 {.tabset .tabset-pills}
### Table
```{r results='asis'}
support1_tbl <- tableby(org_type~
                    stance_1_cat3, data=com1df, control=mycontrols)

summary(support1_tbl, labelTranslations = mylabels, pfootnote=TRUE)
```


### Figure 
```{r fig.height=6}
com1df %>%
  group_by(org_type, stance_1_cat3, .drop=FALSE) %>%
  summarise(n=n()) %>%
  group_by(org_type) %>%
  filter(org_type!="other") %>%
  mutate(pct = n/sum(n)) %>%
  ggplot() +
  geom_col(aes(y=pct, x = stance_1_cat3, fill = stance_1_cat3), position="dodge") +
  labs (x = "", y = "Percentage", fill=" ") +
  geom_text(aes(y=pct, x = stance_1_cat3, label=paste0(round(pct*100, 0), "%"), group=org_type), position = position_dodge(0.9), vjust=1.2, size=3, color="white") +
  scale_y_continuous(labels=scales::percent_format()) + 
    theme(legend.position="bottom", axis.ticks.x=element_blank(), axis.text.x=element_blank()) +
  facet_wrap(~org_type, nrow=2, scale="free_x", labeller = labeller(org_type = label_wrap_gen(width = 25))) +
  ggtitle("Stance by organization type, 2017")

```

## 2020 {.tabset .tabset-pills}
### Table
```{r results='asis'}
support2_tbl <- tableby(org_type~
                    stance_1_cat3, data=com2df, control=mycontrols)

summary(support2_tbl, labelTranslations = mylabels, pfootnote=TRUE)
```


### Figure
```{r fig.height=6}
com2df %>%
  group_by(org_type, stance_1_cat3, .drop=FALSE) %>%
  summarise(n=n()) %>%
  group_by(org_type) %>%
  filter(org_type!="other") %>%
  mutate(pct = n/sum(n)) %>%
  ggplot() +
  geom_col(aes(y=pct, x = stance_1_cat3, fill = stance_1_cat3), position="dodge") +
  labs (x = "", y = "Percentage", fill=" ") +
  geom_text(aes(y=pct, x = stance_1_cat3, label=paste0(round(pct*100, 0), "%"), group=org_type), position = position_dodge(0.9), vjust=1.2, size=3, color="white") +
  scale_y_continuous(labels=scales::percent_format()) + 
    theme(legend.position="bottom", axis.ticks.x=element_blank(), axis.text.x=element_blank()) +
  facet_wrap(~org_type, nrow=2, scale="free_x", labeller = labeller(org_type = label_wrap_gen(width = 25))) +
  ggtitle("Stance by organization type, 2020")

```

## Combined figure

```{r fig.height=8, fig.width=10}
list(com1df, com2df) %>%
  reduce(full_join) %>%
  group_by(year, org_type, stance_1_cat3, .drop=FALSE) %>%
  summarise(n=n()) %>%
  group_by(year, org_type) %>%
  filter(org_type!="other") %>%
  mutate(pct = n/sum(n)) %>%
  ggplot() +
  geom_col(aes(y=pct, x = stance_1_cat3, group = year, fill=as.factor(year)), position="dodge") +
  labs (x = "", y = "Percentage", fill=" ") +
  geom_text(aes(y=pct, x = stance_1_cat3, label=paste0(round(pct*100, 0), "%"), group=year), position = position_dodge(1), vjust=-.35, size=3, color="black") +
  scale_y_continuous(labels=scales::percent_format()) + 
    theme(legend.position="bottom") +
  scale_x_discrete(labels = scales::wrap_format(15)) +
  facet_wrap(~org_type, nrow=2, scale="free_x", labeller = labeller(org_type = label_wrap_gen(width = 25))) +
  ggtitle("Stance by organization type and year")
```

